String Constraints with Regex-Counting and String-Length Solved Efficiently

### 2023-08-18 2023-1-19/sections/cefa.tex
setta2023

In this section, we define the cost-enriched finite state automata (CEFA), which was introduced in \cite{atva2020} and will be used to solve the satisfiability problem of RECL later on. 
%
Intuitively, CEFA adds write-only cost registers to finite state automata. Here by ``write-only'', we mean that the cost registers can only be written/updated but cannot be read; that is, they cannot be used to guard the transitions.

%
%In~\cite{atva2020}, the cost function is defined as a function $\eta: \Sigma \rightarrow \mathbb{N}$. In this paper, we define the cost function as an integer vector whose elements are the incremental value of registers. Furthermore, we add a new linear integer arithmetic constraint $\theta$ to each final state of the CEFA, which restricts the value of registers. Two types of definitions have the same expressive ability on the $SAT_{CL}$ problem.
\begin{definition}[Cost-Enriched Finite Automaton]
  A cost-enriched finite automaton $\aut$ is a tuple $(R, Q, \Sigma, \delta, I, F, \alpha)$ where
  \begin{itemize}
  \item $R = \{r_1, \cdots, r_k\}$ is a finite set of registers, 
    \item $Q, \Sigma, I, F$ are as in the definition of NFA,
%    \item $R = (r_1\cdots r_n)$ is a vector of mutually distinct cost registers,
    \item $\delta \subseteq Q \times \Sigma \times Q \times \Int^R$ is a transition relation, where $\Int^R$ denotes the updates on the values of registers.
%  set whose elements are tuples $(q, c, q', \myvec{v})$ where $q, q'$ are states of $Q$, $c$ is a letter in alphabet $\Sigma\cup\{\epsilon\}$ and $\myvec{v}$ is the cost update function for registers, which is an integer vector whose $i$-th element is the incremental value of register $r_i$.  $(q, a, q', \myvec{v})$ is written as $q\xrightarrow[\myvec{v}]{a} q'$ for readability.
    \item $\alpha \in \Phi(R)$ is an LIA formula specifying an accepting condition.
%    a linear integer arithmetic constraint function on final states. $\theta$ is called \emph{accepting condition}.
  \end{itemize}
\end{definition}
For a CEFA $\aut$, we use $R_\aut$ to denote the set of registers of $\aut$. 
%The definition of CEFA above is slightly different from the definition in~\cite{atva2020} in the sense that accepting conditions on register values
%are attached to final states.

For convenience, from now on, we assume a linear order on $R$ and write $R$ as a vector $\myvec{r} = (r_1, \cdots, r_k)$. Accordingly, we write an element of $\Int^R$ as a vector $(v_1, \cdots, v_k)$, where for each $i \in [k]$, $v_i$ is the update on the value of $r_i$. We also write a transition $(q, a, q', \vec{v}) \in \delta$ as $q \xrightarrow[\vec{v}]{a} q'$.

The semantics of CEFA is defined as follows. Let $\aut = (R, Q, \Sigma, \delta, I, F, \alpha)$ be a CEFA. 
%A \emph{configuration} of $\aut$ is a pair $(q, \vec{v})$ where $q \in Q$ and $\vec{v}$ is a vector denoting the values of registers.  
%An \emph{initial configuration} of $\aut$ is $(q_0, \vec{0})$ with $q_0 \in I$, where the value of each register is zero. 
A \emph{run} of $\aut$ on a string $w = a_1 \cdots a_n$ is a sequence $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ such that $q_0 \in I$ and $q_{i-1} \xrightarrow[\myvec{v_i}]{a_i} q_i$ for each $i \in [n]$. A run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ is \emph{accepting} if $q_n \in F$ and $\alpha(\myvec{v'}/R)$ is true, where $\myvec{v'} = \sum \limits_{j \in [n]} \myvec{v_j}$. The vector $\myvec{v'}= \sum \limits_{j \in [n]} \myvec{v_j}$ is called the \emph{cost} of an accepting run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$. Note that we assume that the initial values of all registers are zero and $\sum \limits_{j \in [n]} \myvec{v_j}$ is the vector of register values after all the transitions in the run are executed. We use $\myvec{v'} \in \aut(w)$ to denote the fact that there is an accepting run of $\aut$ on $w$ whose cost is $\myvec{v'}$.  
We define the semantics of a CEFA $\aut$, denoted by $\Lang(\aut)$, as $\{(w; \myvec{v'}) \mid  \myvec{v'} \in \aut(w)\}$.  In particular, if $I \cap F \neq \emptyset$, then $(\varepsilon; \myvec{0}) \in \Lang(\aut)$. Moreover, we define the \emph{output} of a CEFA $\aut$, denoted by $\cefaout(\aut)$, as $\{\myvec{v'} \mid  \exists w.\ \myvec{v'} \in \aut(w)\}$.

We want to remark that the definition above of CEFA is slightly different from that in \cite{atva2020}, where CEFA did not include accepting conditions.
Moreover, the accepting conditions $\alpha$ in CEFA are defined in a \emph{global} fashion because the accepting condition does not distinguish final states. This technical choice is made so that the determinization and minimization of NFA can be utilized to reduce the size of CEFA in the next section.

@@

The \emph{union} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \cup \aut_2$, is defined in a slightly more involved manner than NFA, as a result of the technical choice that the accepting conditions of CEFA do not distinguish final states. Two fresh auxiliary registers say $r'_1,r'_2 \not \in R_1 \cup R_2$, are introduced so that the accepting condition knows whether a run is from $\aut_1$ or $\aut_2$. Specifically, $\aut_1 \cup \aut_2 = (R', Q', \Sigma, \delta', I', F', \alpha')$, where 
\begin{itemize}
\item $R' = R_1 \cup R_2 \cup \{r'_1, r'_2\}$, $Q' = Q_1 \cup Q_2 \cup \{q'_0\}$ with $q'_0 \not \in Q_1 \cup Q_2$, $I' = \{q'_0\}$, 
%
\item $\delta'$ is the union of $\{(q'_0, a, q'_1, (\myvec{v_1}, \myvec{0}, 1,0)) \mid \exists q_1 \in I_1.\ (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$, $\{(q'_0, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 1)) \mid \exists q_2 \in I_2.\ (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$, $\{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0}, 0, 0)) \mid (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$, and $\{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 0)) \mid (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$, where $(\myvec{v_1}, \myvec{0}, 1,0)$ is a vector that updates $R_1$ by $\myvec{v_1}$, updates $R_2$ by $\myvec{0}$, and updates $r'_1,r'_2$ by $1,0$ respectively. Similarly for $(\myvec{0}, \myvec{v_2}, 0, 1)$, and so on.

\item $F'$ and $\alpha'$ are defined as follows, 
\begin{itemize}
\item if either $I_1 \cap F_1 \neq \emptyset$ and $\alpha_1[\myvec{0}/R_1]$ is true, or $I_2 \cap F_2 \neq \emptyset$ and $\alpha_2[\myvec{0}/R_2]$ is true, then $F' = F_1 \cup F_2 \cup \{q'_0\}$ and $\alpha' = (r'_1 = 0 \wedge r'_2 = 0) \vee (r'_1=1 \wedge \alpha_1) \vee (r'_2=1 \wedge \alpha_2)$, 
%
%\item otherwise, if $I_2 \cap F_2 \neq \emptyset$, then $F' = F_1 \cup F_2 \cup \{q'_0\}$ and $\alpha' = (r'_1 = 0 \wedge r'_2 = 0 \wedge \alpha_2) \vee (r'_1=1 \wedge \alpha_1) \vee (r'_2=1 \wedge \alpha_2)$, 
%
\item otherwise, $F'=F_1 \cup F_2$ and $\alpha' = (r'_1=1 \wedge \alpha_1) \vee (r'_2=1 \wedge \alpha_2)$.
\end{itemize}
\end{itemize}
From the construction, we know that 
$$
\Lang(\aut_1 \cup \aut_2) = 
\left\{(w; \myvec{v}) \left \vert 
\begin{array}{l}
%\myvec{v} \in \Int^{R'}, 
(w; \prj_{R_1}(\myvec{v})) \in \Lang(\aut_1) \mbox{ and } \prj_{R_2}(\myvec{v}) = \myvec{0}, \mbox{ or } \\
(w; \prj_{R_2}(\myvec{v})) \in \Lang(\aut_2) \mbox{ and } \prj_{R_1}(\myvec{v}) = \myvec{0}
\end{array}
\right.
\right\}.
$$

The \emph{intersection} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \cap \aut_2 = (R', Q', \Sigma, \delta', I', F', \alpha')$, is defined in the sequel. 
\begin{itemize}
\item $R' = R_1 \cup R_2$, $Q' = Q_1 \times Q_2$, $I' = I_1 \times I_2$, $F' = F_1 \times F_2$, $\alpha' = \alpha_1 \wedge \alpha_2$, 
%
%\item $\alpha'((q_1, q_2)) = \alpha_1(q_1) \wedge \alpha_2(q_2)$ for each $(q_1, q_2) \in F'$, 
%
\item $\delta'$ comprises the tuples $((q_1, q_2), a, (q'_1, q'_2), (\myvec{v_1}, \myvec{v_2}))$ such that $(q_1,a, q'_1, \myvec{v_1}) \in \delta_1$ and $(q_2,a, q'_2, \myvec{v_2}) \in \delta_2$.
%, where $\myvec{v} \in \Int^{R'}$, $\prj_{R_1}(\myvec{v}))$ (resp. $\prj_{R_2}(\myvec{v}))$) is the restriction of $\myvec{v}$ to the domain $R_1$ (resp. $R_2$). 
\end{itemize}
From the construction, 
$$\Lang(\aut_1 \cap \aut_2) = \{(w; \myvec{v}) \mid \myvec{v} \in \Int^{R'}, (w; \prj_{R_1}(\myvec{v})) \in \Lang(\aut_1) \mbox{ and } (w; \prj_{R_2}(\myvec{v})) \in \Lang(\aut_2)\}.$$ 
Intuitively, $\aut_1 \cap \aut_2$ accepts the words that are accepted by both $\aut_1$ and $\aut_2$ and outputs the costs of $\aut_1$ and $\aut_2$.

The \emph{concatenation} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \concat \aut_2$, is defined similarly as that of NFA, that is, a tuple $(Q', \Sigma, \delta', I', F', \alpha')$, where $Q' = Q_1 \cup Q_2$, $I' = I_1$, $\alpha' = \alpha_1 \wedge \alpha_2$, $\delta' = \{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0})) \mid (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\} \cup \{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2})) \mid (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\} \cup \{(q_1, a, q_2, (\myvec{0}, \vec{v_2})) \mid q_1 \in F_1, \exists q' \in I_2.\ (q', a, q_2, \vec{v_2}) \in \delta_2\}$, moreover, if $I_2 \cap F_2 \neq \emptyset$, then $F'= F_1 \cup F_2$, otherwise, $F'= F_2$. From the construction, 
$$\Lang(\aut_1 \concat \aut_2) = \{(w_1w_2; \myvec{v}) \mid (w_1; \prj_{R_1}(\myvec{v})) \in \Lang(\aut_1), (w_2; \prj_{R_2}(\myvec{v})) \in \Lang(\aut_2)\}.$$

>>>>

In this section, we define the cost-enriched finite state automata (CEFA), which was introduced in \cite{atva2020} and will be used to solve the satisfiability problem of RECL later on. 
%
Intuitively, CEFA adds write-only cost registers to finite state automata. ``write-only'' means that the cost registers can only be written/updated but cannot be read, i.e., they cannot be used to guard the transitions.

%
%In~\cite{atva2020}, the cost function is defined as a function $\eta: \Sigma \rightarrow \mathbb{N}$. In this paper, we define the cost function as an integer vector whose elements are the incremental value of registers. Furthermore, we add a new linear integer arithmetic constraint $\theta$ to each final state of the CEFA, which restricts the value of registers. Two types of definitions have the same expressive ability on the $SAT_{CL}$ problem.
\vspace{-0.5mm}
\begin{definition}[Cost-Enriched Finite Automaton]
  A cost-enriched finite automaton $\aut$ is a tuple $(R, Q, \Sigma, \delta, I, F, \alpha)$ where
  \begin{itemize}
  \item $R = \{r_1, \cdots, r_k\}$ is a finite set of registers, 
    \item $Q, \Sigma, I, F$ are as in the definition of NFA,
%    \item $R = (r_1\cdots r_n)$ is a vector of mutually distinct cost registers,
    \item $\delta \subseteq Q \times \Sigma \times Q \times \Int^R$ is a transition relation, where $\Int^R$ denotes the updates on the values of registers.
%  set whose elements are tuples $(q, c, q', \myvec{v})$ where $q, q'$ are states of $Q$, $c$ is a letter in alphabet $\Sigma\cup\{\epsilon\}$ and $\myvec{v}$ is the cost update function for registers, which is an integer vector whose $i$-th element is the incremental value of register $r_i$.  $(q, a, q', \myvec{v})$ is written as $q\xrightarrow[\myvec{v}]{a} q'$ for readability.
    \item $\alpha \in \Phi(R)$ is an LIA formula specifying an accepting condition.
%    a linear integer arithmetic constraint function on final states. $\theta$ is called \emph{accepting condition}.
  \end{itemize}
\end{definition}
\vspace{-0.5mm}

For convenience, we use $R_\aut$ to denote the set of registers of $\aut$. We assume a linear order on $R$ and write $R$ as a vector $(r_1, \cdots, r_k)$. Accordingly, we write an element of $\Int^R$ as a vector $(v_1, \cdots, v_k)$, where $v_i$ is the update of $r_i$ for each $i \in [k]$. We also write a transition $(q, a, q', \vec{v}) \in \delta$ as $q \xrightarrow[\vec{v}]{a} q'$.
%The definition of CEFA above is slightly different from the definition in~\cite{atva2020} in the sense that accepting conditions on register values
%are attached to final states.

The semantics of CEFA is defined as follows. Let $\aut = (R, Q, \Sigma, \delta, I, F, \alpha)$ be a CEFA. 
%A \emph{configuration} of $\aut$ is a pair $(q, \vec{v})$ where $q \in Q$ and $\vec{v}$ is a vector denoting the values of registers.  
%An \emph{initial configuration} of $\aut$ is $(q_0, \vec{0})$ with $q_0 \in I$, where the value of each register is zero. 
A \emph{run} of $\aut$ on a string $w = a_1 \cdots a_n$ is a sequence $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ such that $q_0 \in I$ and $q_{i-1} \xrightarrow[\myvec{v_i}]{a_i} q_i$ for each $i \in [n]$. A run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$ is \emph{accepting} if $q_n \in F$ and $\alpha(\myvec{v'}/R)$ is true, where $\myvec{v'} = \sum \limits_{j \in [n]} \myvec{v_j}$. The vector $\myvec{v'}= \sum \limits_{j \in [n]} \myvec{v_j}$ is called the \emph{cost} of an accepting run $q_0 \xrightarrow[\myvec{v_1}]{a_1} q_1 \cdots q_{n-1}\xrightarrow[\myvec{v_n}]{a_n} q_n$. Note that the values of all registers are initiated to zero and updated to $\sum \limits_{j \in [n]} \myvec{v_j}$ after all the transitions in the run are executed. We use $\myvec{v'} \in \aut(w)$ to denote the fact that there is an accepting run of $\aut$ on $w$ whose cost is $\myvec{v'}$.  
We define the semantics of a CEFA $\aut$, denoted by $\Lang(\aut)$, as $\{(w; \myvec{v'}) \mid  \myvec{v'} \in \aut(w)\}$.  In particular, if $I \cap F \neq \emptyset$ and $\alpha(\myvec{0}/R)$ is true, then $(\varepsilon; \myvec{0}) \in \Lang(\aut)$. Moreover, we define the \emph{output} of a CEFA $\aut$, denoted by $\cefaout(\aut)$, as $\{\myvec{v'} \mid  \exists w.\ \myvec{v'} \in \aut(w)\}$.

We want to remark that the definition of CEFA above is slightly different from that of \cite{atva2020}, where CEFA did not include accepting conditions.
Moreover, the accepting conditions $\alpha$ in CEFA are defined in a \emph{global} fashion because the accepting condition does not distinguish final states. This technical choice is made so that the determinization and minimization of NFA can be utilized to reduce the size of CEFA in the next section.

@@

The \emph{union} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \cup \aut_2$, is defined in a slightly more involved manner than NFA, as a result of the technical choice that the accepting conditions of CEFA do not distinguish final states. Two fresh auxiliary registers say $r'_1,r'_2 \not \in R_1 \cup R_2$, are introduced so that the accepting condition knows whether a run is from $\aut_1$ (or $\aut_2$). Specifically, $\aut_1 \cup \aut_2 = (R', Q', \Sigma, \delta', I', F', \alpha')$ where 
\begin{itemize}
\item $R' = R_1 \cup R_2 \cup \{r'_1, r'_2\}$, $Q' = Q_1 \cup Q_2 \cup \{q'_0\}$ with $q'_0 \not \in Q_1 \cup Q_2$, $I' = \{q'_0\}$, 
%
\item $\delta'$ is the union of four transitions sets:
\begin{itemize}
  \item $\{(q'_0, a, q'_1, (\myvec{v_1}, \myvec{0}, 1,0)) \mid \exists q_1 \in I_1.\ (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$
  \item $\{(q'_0, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 1)) \mid \exists q_2 \in I_2.\ (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$
  \item $\{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0}, 0, 0)) \mid q_1\not\in I_1.\ (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\}$
  \item $\{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2}, 0, 0)) \mid q_2\not\in I_2.\ (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\}$
\end{itemize}
 where $(\myvec{v_1}, \myvec{0}, 1,0)$ is a vector that updates $R_1$ by $\myvec{v_1}$, updates $R_2$ by $\myvec{0}$, and updates $r'_1,r'_2$ by $1,0$ respectively. Similarly for $(\myvec{0}, \myvec{v_2}, 0, 1)$, and so on.

\item $F'$ and $\alpha'$ are defined as follows, 
\begin{itemize}
\item if $(\epsilon; \myvec{0})$ belongs to $\lan(\aut_1)$ or $\lan(\aut_2)$, i.e., one of the two automata accepts the empty string $\epsilon$, then $F' = F_1 \cup F_2 \cup \{q'_0\}$ and $\alpha' = (r'_1 = 0 \wedge r'_2 = 0) \vee (r'_1=1 \wedge \alpha_1) \vee (r'_2=1 \wedge \alpha_2)$, 
%
%\item otherwise, if $I_2 \cap F_2 \neq \emptyset$, then $F' = F_1 \cup F_2 \cup \{q'_0\}$ and $\alpha' = (r'_1 = 0 \wedge r'_2 = 0 \wedge \alpha_2) \vee (r'_1=1 \wedge \alpha_1) \vee (r'_2=1 \wedge \alpha_2)$, 
%
\item otherwise, $F'=F_1 \cup F_2$ and $\alpha' = (r'_1=1 \wedge \alpha_1) \vee (r'_2=1 \wedge \alpha_2)$.
\end{itemize}
\end{itemize}
From the construction, we know that 
$$
\Lang(\aut_1 \cup \aut_2) = 
\left\{(w; \myvec{v}) \left \vert 
\begin{array}{l}
%\myvec{v} \in \Int^{R'}, 
(w; \prj_{R_1}(\myvec{v})) \in \Lang(\aut_1) \mbox{ and } \prj_{r_1'}(\myvec{v}) = 1, \mbox{ or } \\
(w; \prj_{R_2}(\myvec{v})) \in \Lang(\aut_2) \mbox{ and } \prj_{r_2'}(\myvec{v}) = 1, \mbox{ or } \\
(w; \myvec{v}) = (\epsilon, \myvec{0}) \mbox{ if } \aut_1 \mbox{ or } \aut_2 \mbox{ accepts } \epsilon
\end{array}
\right.
\right\}.
$$ 
Intuitively, $\aut_1 \cup \aut_2$ accepts the words that are accepted by one of the $\aut_1$ and $\aut_2$ and outputs the costs of the corresponding automaton.

The \emph{intersection} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \cap \aut_2 = (R', Q', \Sigma, \delta', I', F', \alpha')$, is defined in the sequel. 
\vspace{-0.5mm}
\begin{itemize}
\item $R' = R_1 \cup R_2$, $Q' = Q_1 \times Q_2$, $I' = I_1 \times I_2$, $F' = F_1 \times F_2$, $\alpha' = \alpha_1 \wedge \alpha_2$, 
%
%\item $\alpha'((q_1, q_2)) = \alpha_1(q_1) \wedge \alpha_2(q_2)$ for each $(q_1, q_2) \in F'$, 
%
\item $\delta'$ comprises the tuples $((q_1, q_2), a, (q'_1, q'_2), (\myvec{v_1}, \myvec{v_2}))$ such that $(q_1,a, q'_1, \myvec{v_1}) \in \delta_1$ and $(q_2,a, q'_2, \myvec{v_2}) \in \delta_2$.
%, where $\myvec{v} \in \Int^{R'}$, $\prj_{R_1}(\myvec{v}))$ (resp. $\prj_{R_2}(\myvec{v}))$) is the restriction of $\myvec{v}$ to the domain $R_1$ (resp. $R_2$). 
\end{itemize}
\vspace{-0.5mm}
From the construction, 
\vspace{-0.5mm}
$$\Lang(\aut_1 \cap \aut_2) = \{(w; \myvec{v}) \mid (w; \prj_{R_1}(\myvec{v})) \in \Lang(\aut_1) \mbox{ and } (w; \prj_{R_2}(\myvec{v})) \in \Lang(\aut_2)\}.$$
\vspace{-0.5mm}
Intuitively, $\aut_1 \cap \aut_2$ accepts the words that are accepted by both $\aut_1$ and $\aut_2$ and outputs the costs of $\aut_1$ and $\aut_2$.

The \emph{concatenation} of $\aut_1$ and $\aut_2$, denoted by $\aut_1 \concat \aut_2$, is defined similarly as that of NFA, that is, a tuple $(Q', \Sigma, \delta', I', F', \alpha')$, where $Q' = Q_1 \cup Q_2$, $I' = I_1$, $\alpha' = \alpha_1 \wedge \alpha_2$, $\delta' = \{(q_1, a, q'_1, (\myvec{v_1}, \myvec{0})) \mid (q_1, a, q'_1, \myvec{v_1}) \in \delta_1\} \cup \{(q_2, a, q'_2, (\myvec{0}, \myvec{v_2})) \mid (q_2, a, q'_2, \myvec{v_2}) \in \delta_2\} \cup \{(q_1, a, q_2, (\myvec{0}, \vec{v_2})) \mid q_1 \in F_1, \exists q' \in I_2.\ (q', a, q_2, \vec{v_2}) \in \delta_2\}$, moreover, if $I_2 \cap F_2 \neq \emptyset$, then $F'= F_1 \cup F_2$, otherwise, $F'= F_2$. From the construction, 
$$\Lang(\aut_1 \concat \aut_2) = \{(w_1w_2; \myvec{v}) \mid (w_1; \prj_{R_1}(\myvec{v})) \in \Lang(\aut_1) \mbox{ and }(w_2; \prj_{R_2}(\myvec{v})) \in \Lang(\aut_2)\}.$$

### 2023-08-18 2023-1-19/sections/conclusion.tex
remove under approximation
setta2023

%TODO
This work proposes an efficient automata-theoretical approach for solving RECL constraints: string constraints with regex-counting and string-length. The approach is based on encoding counting operators in regular expressions by registers symbolically instead of unfolding them explicitly. Moreover, this paper proposes an automata-size reduction technique and an under-approximation-based solution searching technique to improve performance. Finally, we use two benchmark suites comprising 48,834 instances in total to evaluate the performance of our approach. The experimental results show that our approach, with comparable performance, can solve more instances than the state-of-the-art best solvers on RECL constraints. We plan to investigate symbolic approaches to dealing with nested counting operators in future work.

>>>>

%TODO
This work proposes an efficient automata-theoretical approach for solving RECL constraints: string constraints with regex-counting and string-length. The approach is based on encoding counting operators in regular expressions by registers symbolically instead of unfolding them explicitly. Moreover, this paper proposes an automata-size reduction technique to improve performance. Finally, we use two benchmark suites comprising 48,843 instances in total to evaluate the performance of our approach. The experimental results show that our approach, with comparable performance, can solve more instances than the state-of-the-art best solvers on RECL constraints. We plan to investigate symbolic approaches to dealing with nested counting operators in future work.
